\section{Project management}

As alluded to in the previous section, the progress made so far is in accordance with the project timeline set out in the specification, therefore the timetable remains unchanged. Likewise, the objectives do not need refining as remain achievable and relevant. Ideally, the full proof of concept application will be finished by the end of term 1, however due to the large amount of other coursework deadlines, this can be extended to the beginning of term 2 and will not affect the rest of the timeline.

Following the proof of concept, the repeated strategy implementation phase begins where sprints occur in cycles of three weeks. The first week is dedicated to research and planning to find the best strategy for the particular feature that spring. For example, if the focus is investments, then research will be done into how investments affect a user's financial capability and what could be done to aid them. The second week is for development where this chosen approach for that strategy is implemented into the application. This will be done as a separate git branch in accordance with the git flow feature branch practice \cite{GitFlow}. The third week is testing and bug fixing, before being merged into the main application and the cycle begins again. This is appropriate methodology as the requirements at this stage are less clear and quite open, so need to be flexible. Following this, the application will be tested more thoroughly and focus will shift to preparing for the presentation and writing the dissertation.