\section{Legal, Social, Ethical and Professional Issues}
% \section{Legal, Social and Ethical Issues}
The software will have an authentication system enabling users to sign up and log in, making the user experience smooth. Consequently, the current guidance and best practises for security will have to be followed. This includes enforcing a long and complex password for users to avoid unauthorised access from others, but also storing their password and data in a fashion which complies with the GDPR regulations.

As a result of using the Plaid API, no extremely sensitive banking information will be stored locally by me; all this financial data is handled by the Plaid service itself. When the data is displayed to the user, they can be sure that it is verified and secured, so long as the correct flow described in the Plaid documentation is followed during development. Furthermore, when accessing certain products provided by Plaid, steps will be taken to avoid getting unnecessary data, for example when accessing an account's transactions the account number can be displayed as only the last few digits as to avoid vulnerabilities.

The biggest issue the software must avoid is ensuring that the strategies and suggestions are not considered financial advice. To mitigate this, research will be done into knowing the boundary between advice and guidance. The functionality on the website which helps individuals become more financially capable must be opt-in as to avoid pushing suggestions onto users because it may overwhelm them and is against the laws set out by the Financial Conduct Authority.